Object-Oriented Internet - Azure Interoperability

### 2020-11-25 Latex/Manuscript.tex
Update Manuscript.tex

In the final deployment architecture (Fig. \ref*{figure4.ImplementationArchitecture}) the \textit{Consumer} role has been realized by the \textit{PartDataManagementSetup} that is derived from \textit{DatManagementSetup} embedded in the library \textit{Networking} removed from this diagram for the sake of simplicity. It is a basic step for implementation of the \textit{Consumer} role functionality. The class \textit{PartDataManagementSetup} initializes all properties, which are injection points of all parts composing this role. It extents functionality of the \textit{DatManagementSetup} based on the following associated classes

@@

In this case, the implementation of the \textit{IConfigurationFactory} interface is based entirely on the \textit{Networking} library. The implementation provided by the library is generic, but it is flexible enough to meet all the requirements in this case and should not be considered for further modification. It is ready to provide all necessary configuration parameters to establish semantic and security contexts related to Azure interoperability.

@@

\begin{itemize}
      \item \textit{Devices} - Service SDK for Azure IoT Devices
      \item \textit{Devices.Client} - Device SDK for Azure \textit{IoT\ Hub}
      \item \textit{Devices.Shared} - Common code for Azure IoT Device and Service SDK
      \item \textit{Devices.Provisioning.Client} - Provisioning Device Client SDK for Azure IoT Devices
      \item \textit{Devices.Provisioning.Transport.Amqp} - Provisioning Device Client AMQP Transport for Azure IoT Devices
      \item \textit{Devices.Provisioning.Transport.Http} - Provisioning Device Client HTTP Transport for Azure IoT Devices
      \item \textit{Devices.Provisioning.Transport.Mqtt} - Provisioning Device Client MQTT Transport for Azure IoT Devices
\end{itemize}

>>>>

In the final deployment architecture (Fig. \ref*{figure4.ImplementationArchitecture}) the \textit{Consumer} role has been realized by the \textit{PartDataManagementSetup} that is derived from \textit{DataManagementSetup} embedded in the library. \textit{Networking} was removed from this diagram for the sake of simplicity. Invoking \textit{PartDataManagementSetup} is the first step for bootstrapping the \textit{Consumer} role functionality. This class initializes all properties, which are injection points of all parts composing this role. It extents functionality of the \textit{DataManagementSetup} based on the following associated classes:

@@

In this case, the implementation of the \textit{IConfigurationFactory} interface is based entirely on the \textit{Networking} library. The implementation provided by the library is generic, but it is flexible enough to meet all the requirements which warrants no need of further modifications. It is ready to provide all necessary configuration parameters to establish semantic and security contexts related to Azure interoperability.

@@

\begin{itemize}
      \item \textit{Devices} - Service SDK for Azure IoT Devices
      \item \textit{Devices.Client} - Device SDK for Azure \textit{IoT\ Hub} including dependencies implementing MQTT and AMQP communication
      \item \textit{Devices.Shared} - Common code for Azure IoT Device and Service SDK
      \item \textit{Devices.Provisioning.Client} - Provisioning Device Client SDK for Azure IoT Devices
      \item \textit{Devices.Provisioning.Transport.Amqp} - Provisioning Device Client AMQP Transport for Azure IoT Devices
      \item \textit{Devices.Provisioning.Transport.Http} - Provisioning Device Client HTTP Transport for Azure IoT Devices
      \item \textit{Devices.Provisioning.Transport.Mqtt} - Provisioning Device Client MQTT Transport for Azure IoT Devices
\end{itemize}
